Timeliness of security updates for Android

### 2014-10-30 securityupdates.tex
Don't talk about things we promised not to talk about

\subsection{Changes in the \da\ sample}
The \da\ data is mostly generated by devices which have the \da\ app installed because their owner happened to come across the app on Google Play as there has been no advertising and little other attempts to increase usage.
However two collaborations with network operators to install \da\ on customer devices resulted in large numbers of new \da\ users coming from particular areas and network operators.
`n telenor' and `grameenphone' from Table \ref{tab:sec_operator} are big operators in the \da\ data because of their collaboration, in particular `n telenor' conducted a study in Norway with 654 installs of \da\ and `grameenphone' conducted a study in Bangladesh where 2463 users installed \da.
This is responsible for the sudden change in distribution of OS versions in \da\ shown towards the end of Figures \ref{fig:norm_os}, \ref{fig:nvulnerabilities_heat} and \ref{fig:proportioninsecure} as for that period Bangladeshi users contributed over half of the \da\ data.
We could normalise out the influence of the Bangladeshi users, however they are Android users too and they also need security updates.

>>>>

\subsection{Changes in the \da\ sample}
The \da\ data is mostly generated by devices which have the \da\ app installed because their owner happened to come across the app on Google Play as there has been no advertising and little other attempts to increase usage.
However two collaborations with network operators to install \da\ on customer devices resulted in large numbers of new \da\ users coming from particular areas and network operators.
One study was conducted in Norway with 654 installs of \da\ and one was conducted in Bangladesh where 2463 users installed \da.
This is responsible for the sudden change in distribution of OS versions in \da\ shown towards the end of Figures \ref{fig:norm_os}, \ref{fig:nvulnerabilities_heat} and \ref{fig:proportioninsecure} as for that period Bangladeshi users contributed over half of the \da\ data.
We could normalise out the influence of the Bangladeshi users, however they are Android users too and they also need security updates.
